Methods to prioritise pop-up active transport infrastructure

### 2020-05-09 article.Rmd
Explain lane calculation - cc @mem48

An important distinction when developing methods for automated analysis of transport networks is the level of analysis.

>>>>

Geographic analysis alone is insufficient to identify candidates for pop-up infrastructure.
At a time of reduced motor traffic, fewer lanes dedicated for motor traffic are needed.
Based on this observation, we defined roads with a 'spare lane' as those on which there is more than one lane in either direction.
This definition assumes no reduction in mobility for motor vehicles (making twoway lanes oneway is another option not explored in this analysis).

To identify road sections on which there is a spare lane we developed a simple algorithm that takes the OSM variable [`lanes`](https://wiki.openstreetmap.org/wiki/Key:lanes)  if it is present and, if not, derives the number from the highway type and presence/absence of bus lanes.

<!-- Note this could be a function in an R packge.. -->

reallocated road space in particular
An important distinction when developing methods for automated analysis of transport networks is the level of analysis.
